Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-04-08 doc/manuscript_hkk_drought_sensitivity.Rmd
Update manuscript_hkk_drought_sensitivity.Rmd

We analysed data from manual dendrometer band censuses from 2008-2023 in the Huai Kha Khaeng ForestGEO plot (15.6324 N, 99.217 E), hereafter "HKK", in the Huai Kha Khaeng Wildlife Sanctuary, Uthai Thani, Thailand.
This is a 50-hectare plot in mixed deciduous tropical forest, with a mean annual temperature of 1400 mm and a strong dry season from November to April [@anderson-teixeira_ctfsforestgeo_2015].
The dominant canopy species are _Hopea odorata_, _Vatica harmandiana_, _Dipterocarpus alatus_ and _Tetrameles nudiflora_ and lower layers of the canopy are dominated by sub-canopy evergreen and deciduous species like _Miliusa horsfieldii_ and _Polyalthia viridis_. 
Long-term analysis of tree-ring data shows that tree growth at Huai Kha Khaeng has been influenced by temperature and rainfall [@vlam_temperature_2014].

>>>>

Our study site was the Huai Kha Khaeng ForestGEO plot (15.6324 N, 99.217 E), hereafter "HKK", in the Huai Kha Khaeng Wildlife Sanctuary, Uthai Thani, Thailand.
This is a 50-hectare plot in mixed deciduous tropical forest, with a mean annual temperature of 1400 mm and a strong dry season from November to April [@anderson-teixeira_ctfsforestgeo_2015].
The dominant canopy species are _Hopea odorata_, _Vatica harmandiana_, _Dipterocarpus alatus_ and _Tetrameles nudiflora_ and lower layers of the canopy are dominated by sub-canopy evergreen and deciduous species like _Miliusa horsfieldii_ and _Polyalthia viridis_. 
Long-term analysis of tree-ring data shows that tree growth at Huai Kha Khaeng has been influenced by temperature and rainfall [@vlam_temperature_2014].
